---
title: "Neurohackademy 2020 MRI Overview Project"
---

<!-- output: -->
<!--   prettydoc::html_pretty: -->
<!--     theme: architect -->
<!--     highlight: github -->
<!--     toc: true -->

<div style="margin-bottom:100px;">
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
</div>

# Overview

Welcome to the mri overview in flowcharts project. Our goal: Bring newcomers together (maybe with some experienced coders!) to develop some flowcharts and/or overview materials that will increase our understanding of the start-to-finish MRI/fMRI/DTI analysis process by collaborating on interactive flowcharts, which we hope can be shared more broadly to help others similarly understand how these processes flow at a macro level. 

## Collaborators


| Name             | Role     | email                      | GitHub    |     |
| ---------------- | -------- | -------------------------- | --------- | --- |
| Annalysa Lovos   | Lead     | aklovos@email.arizona.edu  | annalysa  |     |
| Amelia Miramonti | Co-Lead  | amelia.miramonti@gmail.com | amelia-m  |     |
| Stepheni Uh      |          |                            | stephuh2  |     |
| Allison Londeree |          | alonderee@gmail.com        | londeree4 |     |
| Nazek Queder     |          | nqueder@hs.uci.edu         | nqueder   |     |
| Jinyi Hung       |          | jinyihung@gmail.com        | jinyihung |     |
| Tuba Sahin       |          | tubasahin.psyc@gmail.com   | tubapona  |     |
| Hulya Aldemir    |          | hulyaald@gmail.com         | hulyaald  |     |
| Dara Ghahremani  |          | darag@ucla.edu             | daraucla  |     |
| Neha Sara John   |          | nehasjohn1d@gmail.com      | NSJohn    |     |
| Ginnie Kim       |          |ginnie.kim@nationwidechildrens.org| ginniekim|  |




<div style="margin-bottom:50px;">
</div>

```{r, echo=FALSE, warning=FALSE}
#Data Wrangling
library(dplyr)
#Run library collapsible Tree
library("collapsibleTree")
# gsheet helps load in google data
library(gsheet)
# DT allows for interactive table
library(DT)
#Read in csvs (for the time being until everything is on drive)
library(readr)

```


## fMRI preprocessing steps {.tabset .tabset-fade}
<div style="margin-bottom:50px;">
</div>
### Flow chart
```{r, echo=FALSE, results="hide"}
#load in data
preprocessing <- read_csv("preprocessing.csv")

```

```{r, echo=FALSE}
collapsibleTree(preprocessing, c("Resource", "Link"), collapsed = FALSE)
```

### Resources
<div style="margin-bottom:50px;">
</div>


## fMRI post-processing steps {.tabset .tabset-fade}
<div style="margin-bottom:50px;">
</div>
### Flow chart
```{r, echo=FALSE, results="hide"}
#Here we can organize the nodes
org <- data.frame(
  Manager = c(
    NA, "Ana", "Ana", "Bill", "Bill", "Bill", "Claudette", "Claudette", "Danny",
    "Fred", "Fred", "Grace", "Larry", "Larry", "Nicholas", "Nicholas"
  ),
  Employee = c(
    "Ana", "Bill", "Larry", "Claudette", "Danny", "Erika", "Fred", "Grace",
    "Henri", "Ida", "Joaquin", "Kate", "Mindy", "Nicholas", "Odette", "Peter"
  ),
  Title = c(
    "President", "VP Operations", "VP Finance", "Director", "Director", "Scientist",
    "Manager", "Manager", "Jr Scientist", "Operator", "Operator", "Associate",
    "Analyst", "Director", "Accountant", "Accountant"
  )
)


```

```{r, echo=FALSE}
collapsibleTree(org, c("Manager", "Employee"), collapsed = FALSE)
```

### Resources
<div style="margin-bottom:50px;">
</div>


# Vocab
```{r, echo = FALSE}
#load in most recent vocab URL
url <- 'docs.google.com/spreadsheets/d/1U3Qi4Ns4POn9R8m0SEua6zU0cO5jjseMq3WrctPEtyo/edit?usp=slack&ts=5f24816f'
#make into sheet
vocab <- gsheet2tbl(url)
#remove url creation columns
selectvocab <- select(vocab, -c("link title","raw url"))


#display interactive plot
datatable(selectvocab,
          escape = F,
          rownames = F, 
          extensions = 'RowGroup', 
          options = list(rowGroup = list(dataSrc=c(0)),
                         columnDefs = list(list(visible=FALSE, targets=c(0)))
                         )
          )

```

