---
title: "Neurohackademy 2020 MRI Overview Project"
---

<div style="margin-bottom:100px;">
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
</div>

```{r, echo=FALSE, warning=FALSE}
# First Time editing this site? Uncomment (remove the #) and run this line first! 
#install.packages("dplyr","collapsibleTree","gsheet","DT","readr","prettydoc")
```

# Overview

Welcome to the MRI overview in flowcharts project. Our goal: Bring newcomers together (maybe with some experienced coders!) to develop some flowcharts and/or overview materials that will increase our understanding of the start-to-finish MRI/fMRI/DTI analysis process by collaborating on interactive flowcharts, which we hope can be shared more broadly to help others similarly understand how these processes flow at a macro level. 

## Collaborators


| Name             | Role     | email                             | GitHub    | Institution  |
| ---------------- | -------- | --------------------------------- | --------- | ------------ |
| Annalysa Lovos   | Lead     | aklovos@email.arizona.edu         | annalysa  | University of Arizona           |
| Amelia Miramonti | Co-Lead  | amelia.miramonti@gmail.com        | amelia-m  | University of Nebraska - Lincoln|
| Stepheni Uh      |          | stepheni.uh@mrc-cbu.cam.ac.uk     | stephuh2  | University of Cambridge         |
| Allison Londeree | Co-Lead  | alonderee@gmail.com               | londeree4 | The Ohio State University       |
| Nazek Queder     |          | nqueder@hs.uci.edu                | nqueder   | UC Irvine                       |
| Jinyi Hung       |          | jinyihung@gmail.com               | jinyihung |              |
| Tuba Sahin       |          | tubasahin.psyc@gmail.com          | tubapona  |              |
| Hulya Aldemir    |          | hulyaald@gmail.com                | hulyaald  |              |
| Dara Ghahremani  |          | darag@ucla.edu                    | daraucla  | UC Los Angeles                  |
| Neha Sara John   |          | nehasjohn1d@gmail.com             | NSJohn    |              |
| Ginnie Kim       |          |ginnie.kim@nationwidechildrens.org | ginniekim | Nationwide Children's Hospital  |




<div style="margin-bottom:50px;">
</div>


```{r, echo=FALSE, warning=FALSE, message=FALSE}
#Data Wrangling
library(dplyr)
#Run library collapsible Tree
library("collapsibleTree")
# gsheet helps load in google data
library(gsheet)
# DT allows for interactive table
library(DT)
#Read in csvs (for the time being until everything is on drive)
library(readr)
```


## sMRI Steps {.tabset .tabset-fade}
<div style="margin-bottom:50px;">
</div>
### Flow chart
```{r, echo=FALSE, results="hide"}

#load in most recent vocab URL
contenturl <- 'https://docs.google.com/spreadsheets/d/1OS48G1jEBcArDIN76jh5PFHGoJSeqfGSTE23ve7lfjk/edit?usp=sharing'
#make into sheet
sMRI <- gsheet2tbl(contenturl)

```

```{r, echo=FALSE}
collapsibleTree(sMRI, c("Section", "Node"), collapsed = FALSE)
```

### Resources
<div style="margin-bottom:50px;">
</div>


## DTI Steps {.tabset .tabset-fade}
<div style="margin-bottom:50px;">
</div>
### Flow chart
```{r, echo=FALSE, results="hide"}
  #load in most recent vocab URL
contenturl <- 'https://docs.google.com/spreadsheets/d/1OS48G1jEBcArDIN76jh5PFHGoJSeqfGSTE23ve7lfjk/edit#gid=2105350491'
#make into sheet
DTI <- gsheet2tbl(contenturl)

```

```{r, echo=FALSE}
#collapsibleTree(org, c("Manager", "Employee"), collapsed = FALSE)
collapsibleTree(DTI, c("Section", "Node"), collapsed = FALSE)
```

### Resources
<div style="margin-bottom:50px;">
</div>

## rs fMRI {.tabset .tabset-fade}
<div style="margin-bottom:50px;">
</div>
### Flow chart
```{r, echo=FALSE, results="hide"}
  #load in most recent vocab URL
contenturl <- 'https://docs.google.com/spreadsheets/d/1OS48G1jEBcArDIN76jh5PFHGoJSeqfGSTE23ve7lfjk/edit#gid=1662967562'
#make into sheet
rsfMRI <- gsheet2tbl(contenturl)

```

```{r, echo=FALSE}
#collapsibleTree(org, c("Manager", "Employee"), collapsed = FALSE)
collapsibleTree(rsfMRI, c("Section", "Node"), collapsed = FALSE)
```

### Resources
<div style="margin-bottom:50px;">
</div>

## task fMRI {.tabset .tabset-fade}
<div style="margin-bottom:50px;">
</div>
### Flow chart
```{r, echo=FALSE, results="hide"}
contenturl1 <- 'https://docs.google.com/spreadsheets/d/1OS48G1jEBcArDIN76jh5PFHGoJSeqfGSTE23ve7lfjk/edit#gid=1730333169'
#make into sheet
taskfMRI <- gsheet2tbl(contenturl1)

```

```{r, echo=FALSE}
collapsibleTree(taskfMRI, c("Section", "Node"), collapsed = FALSE)
```

### Resources
<div style="margin-bottom:50px;">
</div>

# Vocab
```{r, echo = FALSE}
#load in most recent vocab URL
vocaburl <- 'https://docs.google.com/spreadsheets/d/1U3Qi4Ns4POn9R8m0SEua6zU0cO5jjseMq3WrctPEtyo/edit#gid=0'
#make into sheet
vocab <- gsheet2tbl(vocaburl)
#remove url creation columns
selectvocab <- select(vocab, -c("link title","raw url"))


#display interactive plot
datatable(selectvocab,
          escape = F,
          rownames = F, 
          extensions = 'RowGroup', 
          options = list(rowGroup = list(dataSrc=c(0)),
                         columnDefs = list(list(visible=FALSE, targets=c(0)))
                         )
          )

```

